Hydras \& Co.

### 2023-05-21 doc/chapter-fol.tex
change notations of fol-variables

@@

\subsection{Examples}
\label{sect:folFormExamples}

@@

@@

\subsection{Bound variables}

\subsection{Decidability of equality}

Under the assumption that equality is decidable on 
function and relation symbols of any language $L$,
we get decidability of equality on terms and formulas.
Because of dependent types, the proofs are quite long and technical. The reader may consult them in \href{../theories/html/hydras.Ackermann.fol.html}{Ackermann.fol}

@@

@@

@@

@@

\inputsnippets{LNN_Examples/uglyF0a}

>>>>

\subsubsection{Bound variables}

  \index{ackermann}{Projects}
  \begin{project}
 Use a HOAS representation for FOL terms and formulas (without breaking proof scripts).   
  \end{project}

@@

\subsection{Examples}

@@

\label{sect:folFormExamples}

@@

\subsection{On variables}

\begin{todo}
  Difference from HOAS. Free and bound occurrences.
\end{todo}

\subsection{Decidability of equality}
Let $L$ be a language, and let us assume that equality 
of function and relation symbols of $L$ are decidable.
Under this assumption, equality of terms and formulas over $L$ is decidable too.

Because of dependent types, the proofs are quite long and technical. The reader may consult them in \href{../theories/html/hydras.Ackermann.fol.html}{Ackermann.fol}

@@

\inputsnippets{FolExamples/substNotStructural}

@@

\begin{todo}
Link to folProp.v
\end{todo}

@@

\subsection{Multiple substitutions}

\begin{todo}
Link to subAll.v
\end{todo}

@@

\begin{todo}
Fix the issue about the way formulas are printed (mix of different scopes).
\end{todo}
\inputsnippets{LNN_Examples/uglyF0a}
